---
title: "Analysis on Shakespeare"
author: "Shihua Lu"
date: "`r lubridate::today()`"
output: 
   github_document:
     toc: true
     theme_set(theme_minimal())
---

```{r setup, include=FALSE}
# set options
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
library(tidyverse)
library(tidytext)
library(stringr)
library(tm)
library(wordcloud)
library(ggplot2)
library(dplyr)
```

For HW09, I am doing a sentiment analysis for Shakespeare's works. I have chosen three tragedies: Macbeth, Romeo and Juliet, Hamlet and three comedies: Midnight Summer's Dream, As you Like it, The Merchant of Venice. The goal of this project is to see whether the results of my sentiment analysis can show if a play is a tragedy or comedy. The definition of what a tragedy is is always under debate in the field of Art, film studies, Aesthetics and philosophy. Sometimes I get a little bored, just for reading too much theoretical content. Let's see if the debate can be solved by data analysis. 

# load data 
```{r load data, warning = FALSE}
# Tragedies
romeo <- read.delim("The Tragedy of Romeo and Juliet.txt")
macbeth <- read.delim("Macbeth")
hamlet <- read.delim("Hamlet")
# Comedies
asyoulikeit <- read.delim("As You Like It")
midnight <- read.delim("midnight summer")
venice <- read.delim("The Merchant of Venice ")
```
# create corpus 
```{r corpus, warning=FALSE}
preprocessing = function (doc){
   doc = gsub("[^[:alnum:]]"," ",doc)
   #create corpus
   corpus = Corpus(VectorSource(doc))
   #Removal of punctuation
   corpus = tm_map(corpus, removePunctuation)
   #Removal of numbers
   corpus = tm_map(corpus, removeNumbers)
   #Conversion to lower case
   corpus = tm_map(corpus, content_transformer(tolower)) 
   #customize my stopwords
   mystopword = data("stop_words")
   #Removal of stopwords
   corpus = tm_map(corpus, removeWords, c(stopwords("english"),mystopword))
   return(corpus)
}
romeo.cleaned = preprocessing(romeo)
macbeth.cleaned = preprocessing(macbeth)
hamlet.cleaned = preprocessing(hamlet)
asyoulikeit.cleaned = preprocessing(asyoulikeit)
midnight.cleaned = preprocessing(midnight)
venice.cleaned = preprocessing(venice)
```
# Data Visualization: word cloud
```{r, warning=FALSE}
par(mfrow=c(2,3)) 
par(mar=c(2, 3, 2, 3)) # Set the plot margin
par(bg="black") # set background color as black
par(col.main="white") # set title color as white
wordcloud(romeo.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("Romeo and Juliet")
wordcloud(macbeth.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("Macbeth")
wordcloud(hamlet.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("Hamlet")
wordcloud(asyoulikeit.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("As You Like It")
wordcloud(midnight.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("Midnight Summer's Dream")
wordcloud(venice.cleaned, scale=c(4,.5),min.freq=3, max.words=Inf, random.order=F, 
           colors = brewer.pal(8, "Set3"))   
title("The Merchant of Venice")

```
# Data Visualization: Word Frequency
```{r word frequency, warning=FALSE}
romeo.dtm = DocumentTermMatrix(romeo.cleaned)
 findFreqTerms(romeo.dtm, 5)
macbeth.dtm = DocumentTermMatrix(macbeth.cleaned)
 findFreqTerms(macbeth.dtm, 5)
hamlet.dtm = DocumentTermMatrix(hamlet.cleaned)
 findFreqTerms(hamlet.dtm, 5)
asyoulikeit.dtm = DocumentTermMatrix(asyoulikeit.cleaned)
 findFreqTerms(asyoulikeit.dtm, 5)
midnight.dtm = DocumentTermMatrix(midnight.cleaned)
 findFreqTerms(midnight.dtm, 5)
venice.dtm = DocumentTermMatrix(venice.cleaned)
 findFreqTerms(venice.dtm, 5)
## visualization 
par(mfrow=c(2,3))
par(bg="white")
par(col.main="black")
 freq = sort(colSums(as.matrix(romeo.dtm)), decreasing=TRUE) 
 barplot(freq[1:10],col=rev(brewer.pal(9, "GnBu")), horiz=TRUE)
 title("Romeo and Juliet")
 freq = sort(colSums(as.matrix(macbeth.dtm)), decreasing=TRUE) 
 barplot(freq[1:10], col=rev(brewer.pal(9, "GnBu")), horiz=TRUE)
 title("Macbth")
 freq = sort(colSums(as.matrix(hamlet.dtm)), decreasing=TRUE) 
 barplot(freq[1:10], col=rev(brewer.pal(9, "GnBu")), horiz=TRUE)
 title("Hamlet")
freq = sort(colSums(as.matrix(asyoulikeit.dtm)), decreasing=TRUE) 
 barplot(freq[1:10],col=rev(brewer.pal(9, "PuRd")), horiz=TRUE)
 title("As You Like It")
 freq = sort(colSums(as.matrix(venice.dtm)), decreasing=TRUE) 
 barplot(freq[1:10], col=rev(brewer.pal(9, "PuRd")), horiz=TRUE)
 title("The Merchant of Venice")
 freq = sort(colSums(as.matrix(midnight.dtm)), decreasing=TRUE) 
 barplot(freq[1:10], col=rev(brewer.pal(9, "PuRd")), horiz=TRUE)
 title("The Midnight Summer's Dream")
```
# Sentiment Analysis
## sentiment score - Bing
```{r}
# download sentiment datasets
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

GetSentiment <- function(playname){
  playname %>% 
    unnest_tokens(word, Text) %>%
    inner_join(get_sentiments("bing")) %>%# pull out only sentiment words
      count(sentiment) %>% # count the # of positive & negative words
      spread(sentiment, n, fill = 0) %>% # made data wide rather than narrow
      mutate(sentiment = positive - negative) %>% # # of positive words - # of negative owrds

    # return our sentiment dataframe
    return(sentiment)
}
romeo_score = GetSentiment(romeo),
hamlet_score = GetSentiment(hamlet),
macbeth_score = GetSentiment(macbeth),
asyoulikeit_score = GetSentiment(asyoulikeit),
midnight_score = GetSentiment(midnight),
venice_score = GetSentiment(venice)

sentimentscore <- tribble(
  ~name, ~negative, ~positive, ~sentiment,
  "Hamlet", 1321, 1339, 18,
  "Macbeth", 530, 498, -32,
  "Romeo and Juliet", 1282, 1202, -80,
  "Midnight Summer's Dream", 682, 790, 108,
  "The Merchant of Venice", 462, 651, 189,
  "As You Like It", 832, 1106, 274
)
sentimentscore %>%
  ggplot(aes(x = name)) + 
  geom_line(mapping = aes(y = negative, group=1, color = "negative")) +
  geom_line(mapping = aes(y = positive, group=1, color = "positive" )) +
  geom_line(mapping = aes(y = sentiment, group=1, color = "sentiment")) +
  labs(title = "Sentiment Analysis Score",
        subtitle = "Using BING package",
        x = "play names",
        y = "Score")
  
```
## top emotional words - NRC
```{r}
nrc_plot = function(playname){  
  playname %>% 
    unnest_tokens(word, Text) %>%
    inner_join(get_sentiments("nrc")) %>%
   count(word, sentiment, sort = TRUE) %>%
   group_by(sentiment) %>%
   slice_max(n, n = 10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
   geom_col(show.legend = FALSE) +
   facet_wrap(vars(sentiment), scales = "free_y") +
   labs(title = "Number of Occurence of Top Emotional Words",
        x = "Number of Occurence",
        y = NULL)
}
nrc_plot(venice)
nrc_plot(romeo)
nrc_plot(macbeth)
nrc_plot(asyoulikeit)
nrc_plot(hamlet)
nrc_plot(midnight)
```
##
```{r}

```